\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[english]{isodate}
\usepackage[parfill]{parskip}

\usepackage{graphicx}
\graphicspath{ {./images/} }

\usepackage{pdfpages}
\usepackage{setspace}
\usepackage{amsmath}
\usepackage{listings}
\usepackage{color}

\renewcommand\lstlistingname{Quelltext} % Change language of section name

\lstset{ % Setup for typing starlet code
	language=c,
	basicstyle=\small\sffamily,
	numbers=left,
 	numberstyle=\tiny,
	frame=tb,
	tabsize=2,
	columns=fixed,
	showstringspaces=false,
	showtabs=false,
	keepspaces,
	commentstyle=\color{red},
	keywordstyle=\color{blue}
}

\title{%
  \huge Murders Analytics \\
\large A full stack web presentation for murders data}

\author{Kouveris N. Dimitrios, 2730 \\
Neiros Konstantinos, 1234 \\
Papagianni Ioannina, 1234}

\date{2019\\February}

\begin{document}
% cover page
\pagenumbering{gobble}
\maketitle
\newpage

% settings for the document
\pagenumbering{arabic}
\doublespacing

\tableofcontents
\singlespacing

\newpage

\section{Introduction}
Murders analytics is a full stack web application built as a project on advanced
database technologies and applications course at the department of Computer Science
and Engineering, University of Ioannina. The main purpose of this application is
to provide a web interface for interacting with a database and creating charts
that provide useful analytics related to murders.

\section{Application parts}
The application consists of a dedicated database server, a web application API
server and a static files server.

\subsubsection{Database}
The database server is a dedicated server on which the main running application
is a MySql database server. There are many choices for a MySql ranging from linux
to windows. Our choice was Ubuntu 18.04.2 LTS as a database server.

\subsubsection{Backend - API}
The API server is used for direct communication with the database. The API 
is written in node.js.

\subsubsection{Frontend}
The Static server is used for serving the frontend files and fetching data from
the API. Frontend static files are html, css, javascript and media files served by NGINX.


\newpage
\section{Server configuration}

\subsubsection{Database}
Database is hosted on Ubuntu 18.04.2 LTS. Has 1 CPU Core and 1 GB RAM.
Host: 192.168.1.10\\
User: Ken\\
Password: 123456

\begin{verbatim}
apt install mysql-server
mysql_secure_installation
# user = root
# password = 12345678
systemctl enable mysql

ufw allow 3306

vim /etc/mysql/mysql.conf.d/mysqld.cnf
# bind-address=192.168.1.10

mysql -u root -p
> CREATE USER 'sysdba'@'%' IDENTIFIED BY '12345678aA!';
> GRANT ALL PRIVILEGES ON *.* TO 'sysdba'@'%' WITH GRANT OPTION;
> FLUSH PRIVILEGES;

\end{verbatim}


\end{document}
